The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-22 project/paper/method-of-moments.tex
Tweaks to method of moments section.

\subsection{The Moments of the Binomial}

@@

a fact we will need for the third central moment. We will also need $E(B^3)$,
which we will get via the third factorial moment:

@@

\subsection{The Moments of the Skew Normal}

@@

We can see that $g(v)$ is increasing in $v$, which is always $\geq 1$.
Therefore:

>>>>

\subsection{The Moments of the Binomial Distribution}

@@

a fact we will need for the third central moment.

We will also need $E(B^3)$, which we will get via the third factorial moment:

@@

\subsection{The Moments of the Skew Normal Distribution}

@@

We can see that $g(v)$ is increasing in $v = \frac{1+\lambda^2}{\lambda^2} \geq
1$. Therefore:
